---
title: "LeapFrog"
author: "Huf"
date: "2/12/2020"
output: 
  github_document:
    df_print: kable
bibliography: bib.bib
---

<!-- badges: start -->
  [![Travis build status](https://travis-ci.org/bjhufstetler/LeapFrog.svg?branch=master)](https://travis-ci.org/bjhufstetler/LeapFrog)
<!-- badges: end -->
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
LeapFrog is a single agent metaheuristic search algorithm for solving the Travelling Salesman Problem. LeapFrog can be used with non-symmetrical distance matrices, coordinate matrices, or both. The solution method can easily be expanded to solve for other types of shortest-path problems.

Given a distance matrix, coordinate matrix, or both, the `LeapFrog::ImportData()` function will create a LeapFrog class object that can then be used with the LeapFrog algorithm function `LeapFrog::LF()`. 

## Parameters
The LeapFrog algorithm offers the following tunable parameters:

* m: The number of games to be played by the algorithms [1, inf)
* r: The number of rounds in each game [1, inf)
* p: The percentage of available nodes removed in each round (0, 1]
* s: The accuracy of player landing positions in the first round of each game (0, 1]
* a: The decay rate of p as a game is played (0, 1]
* monitor: If TRUE, will print a status message after each game [T, F]

## Example
### Create LeapFrog Class Object
LeapFrog comes with 13 different known TSP instances, sourced from the TSPLIB [@reinelt1991tsplib]. They can be called using

```{r getData}
LeapFrogObject <- LeapFrog::GetData(1)
```

or by using the function
```{r importData, eval = F}
LeapFrog::ImportData(distances = yourDistanceMatrix, coordinates = yourCoordinateMatrix)
```

### Run the LeapFrog Algorithm
Run the LeapFrog algorithm by passing the LeapFrog class object and any parameters.

```{r LF}
LeapFrogOutput <- LeapFrog::LF(LeapFrogObject, m = 10, r = 20, a = .5)
```

## References
